---
  title: "Intro Data Science Asn 1: Jessica Yang"
  output: html_notebook
---
  
Create a R notebook and do the following:

#### Provide links for two online resources where you can get help for R (put the links in the R notebook that you will submit)
https://www.r-project.org/help.html

http://statseducation.com/Introduction-to-R/modules/getting%20started/help/

#### Search online what the following functions do in R: runif, mean, sd
runif : generates n uniform random numbers between 0 and 1. runif(n, a, b) generates n uniform random numbers between a and b .
mean : a vector is calculated using the mean() function. The function accepts a vector as input, and returns the average as a numeric.
sd : find the standard deviation of the values


#### Generate a vector called “mynums” of 10 random numbers from a uniform distribution between 0 and 100

```{r}
mynums <- runif(10, min = 0, max = 100)
print(mynums)

```

#### Display the mean of the generated numbers
```{r}
mean_value <- mean(mynums)
cat("Mean:", mean_value, "\n")
```


#### Display the standard deviation of the generated numbers
```{r}
sd_value <- sd(mynums)
cat("Standard Deviation:", sd_value, "\n")

```


#### Using “If” statement in R, generate a vector of TRUE and FLASE where TRUE corresponds to a value in “mynums” that is within 2 standard deviations from the mean (FALSE corresponds to a value that is not within 2 standard deviations).
```{r}
within_2_sd <- ifelse((mean_value-2*sd_value<= mynums) & (mynums <= mean_value+2*sd_value), TRUE, FALSE)

print(within_2_sd)
```


#### Import the Ads dataset.
```{r}
MyAdsData = read.csv("ads.csv")
```

#### Make two separate pie-charts for two of the variables.
chart one: gender distribution 
```{r}
One_count <- sum(MyAdsData$Gender == 1)
Zero_count <- sum(MyAdsData$Gender == 0)
gender_counts <- c("0" = Zero_count, "1" = One_count)
pie(gender_counts, labels = names(gender_counts), main = "Gender Distribution")
```
chart two: 
```{r}
myTable = table(MyAdsData$Impressions)
pie(myTable, labels = names(myTable), main = "Impressions")
```

#### Save the file as “rmd” and “html”

#### Put both files in a zip file and submit the zip file on learn.